Donor Responses to Civil Society Repression

### 2024-11-05 manuscript.qmd
Update number

Donor countries have a range of possible responses when recipient countries engage in administrative crackdown. Recent research finds that national and multilateral aid agencies are responsive to anti-NGO laws, though often in inconsistent ways [@ChaudhryHeiss:2022a]. @ChristensenWeinstein:2013 show that aid from bilateral donors—or direct country-to-country aid—sees an average decrease of $25–\$50 million after recipient states pass laws that restrict the flow of foreign funds to NGOs. However, aid from multilateral agencies is not affected by these laws. Similarly, @DupuyPrakash:2018 find that the adoption of a restrictive foreign funding law is associated with a 32% decline in aid from bilateral donors, but has no corresponding change in aid from multilateral donors.

>>>>

Donor countries have a range of possible responses when recipient countries engage in administrative crackdown. Recent research finds that national and multilateral aid agencies are responsive to anti-NGO laws, though often in inconsistent ways [@ChaudhryHeiss:2022a]. @ChristensenWeinstein:2013 show that aid from bilateral donors—or direct country-to-country aid—sees an average decrease of $25 million after recipient states pass laws that restrict the flow of foreign funds to NGOs. However, aid from multilateral agencies is not affected by these laws. Similarly, @DupuyPrakash:2018 find that the adoption of a restrictive foreign funding law is associated with a 32% decline in aid from bilateral donors, but has no corresponding change in aid from multilateral donors.
